Human Factors Influencing Visual Statistical Inference

### 2013-09-04 sociology_paper.tex
reference for expectation error added (sensory evaluation techniques)

A lineup can be evaluated by a single person or multiple observers. A distribution \hh{similar to the binomial distribution, but adjusted for dependencies introduced by the lineup scenario,} is used to calculate the $p$-value based on the number of times observers identify the actual data plot, which provides the information needed to make a decision on rejecting or failing to reject the null hypothesis.  Observers should not be aware of the data that constitutes a lineup, and should not have seen the actual data plot before seeing the lineup. This is the reason that in the election example, above, the scenario was explained after the lineup question, in the text.

>>>>

A lineup can be evaluated by a single person or multiple observers. A distribution \hh{similar to the binomial distribution, but adjusted for dependencies introduced by the lineup scenario,} is used to calculate the $p$-value based on the number of times observers identify the actual data plot, which provides the information needed to make a decision on rejecting or failing to reject the null hypothesis.  In order to avoid expectation errors \citep{meilgaard}, observers should not be aware of the data that constitutes a lineup, and should not have seen the actual data plot before seeing the lineup. This is the reason that in the election example, above, the scenario was explained after the lineup question, in the text.
